\documentclass[11pt,a4paper]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{xcolor}

% Define custom colors - more professional dark blue
\definecolor{linkcolor}{HTML}{000000}  % Changed to black for better professionalism
\definecolor{sectioncolor}{HTML}{000000}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{sectioncolor}
}{}{0em}{}[\color{sectioncolor}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{linkcolor}#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{\color{linkcolor}#1} & \textbf{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{\scshape Rachid El Ismaiyly}} \\ \vspace{1pt}
    {\Large \textcolor{sectioncolor}{Frontend Developer}} \\ \vspace{3pt}
    \small 
    \faMapMarker\ Taounate, Morocco \ | \ 
    \faPhone\ +212611563140 \ | \ 
    \faEnvelope\ \href{mailto:relismaiyly@gmail.com}{\textcolor{linkcolor}{relismaiyly@gmail.com}} \ | \
    \faLinkedin\ \href{https://www.linkedin.com/in/rachid-el-isamiyly}{\textcolor{linkcolor}{LinkedIn}} \ | \
    \faGithub\ \href{https://github.com/rel-isma}{\textcolor{linkcolor}{GitHub}}
\end{center}

\section{Summary}
Frontend Developer with hands-on experience in React.js, TypeScript, and UI/UX Design, specializing in building responsive and user-friendly web applications. Proficient in creating interactive dashboards, real-time features, and multi-language support. Skilled in translating design concepts into functional and visually appealing interfaces. I am passionate about learning and continuously improving my skills, dedicating time every day to stay updated with the latest frontend technologies and best practices. Currently advancing my technical expertise at 1337 School (42 Network), I am eager to contribute to innovative frontend projects and grow as a developer in a collaborative and challenging environment.

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{ft\_transcendence} $|$ \emph{React, TypeScript, Django, WebSocket}}{(October 2024 - January 2025)}
\resumeItemListStart
\resumeItem{Developed a full-stack web application featuring a real-time multiplayer ping pong game with a responsive and intuitive UI/UX design.}
\resumeItem{Implemented a real-time chat system with private messaging, notifications, and friend management features using WebSocket.}
\resumeItem{Designed and built an interactive dashboard displaying user statistics, match history, and a leaderboard for competitive tracking.}
\resumeItem{Integrated multi-language support to enhance accessibility for global users.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Prayer Times Web App} $|$ \emph{React.js, RESTful APIs}}{July 2024 - August 2024}
\resumeItemListStart
\resumeItem{Developed a responsive web application using React.js to display prayer times based on geolocation.}
\resumeItem{Integrated external APIs for accurate prayer time calculations and location services.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Inception} $|$ \emph{Docker Containerization, Docker compose}}{May 2024 - June 2024}
\resumeItemListStart
\resumeItem{Developed a scalable web infrastructure using Docker containers, including NGINX, WordPress, and MariaDB.}
\resumeItem{Implemented secure web server configuration with TLSv1.2/TLSv1.3 encryption.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{IRC Server Implementation} $|$ \emph{C++98, Network Programming}}{March 2024 - April 2024}
\resumeItemListStart
\resumeItem{Built a fully functional IRC server handling multiple client connections with non-blocking I/O}
\resumeItem{Implemented robust error handling and connection management systems}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Net\_Practice} $|$ \emph{TCP/IP, Network Configuration}}{September 2023}
\resumeItemListStart
\resumeItem{Configured and troubleshot complex network topologies using TCP/IP protocols}
\resumeItem{Implemented efficient subnetting solutions for optimized network performance}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Minishell} $|$ \emph{C}}{July 2023 - August 2023}
\resumeItemListStart
\resumeItem{Built a mini shell using C, handling user commands, signals, and processes}
\resumeItem{Overcame challenges related to memory management and process synchronization}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Frontend Development:} React.js, TypeScript, JavaScript (ES6+), HTML5, CSS3, Responsive Design, UI/UX Design \\
        \textbf{Backend Development:} Django, Django REST Framework, WebSocket, databases \\
        \textbf{Programming Languages:} JavaScript, TypeScript, C, C++ \\
        \textbf{Tools:} Git, Docker, Figma, Visual Studio Code \\
        \textbf{Other Skills:} Multi-language Support, Real-time Features, Interactive Dashboards \\
        \textbf{Currently Learning:} next.js
    }}
\end{itemize}

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{1337 School (42 Network)}{Sep 2022 - Present}
{Intensive Computer Science Program}{Khouribga, Morocco}
\resumeItemListStart
\resumeItem{Selected for highly competitive coding school affiliated with École 42 Paris.}
\resumeItem{Completed advanced projects in system programming, algorithms, and web development.}
\resumeItemListEnd

\resumeSubheading
{Baccalaureate in Life and Earth Sciences}{2020 - 2021}
{High School Diploma}{Taounate, Morocco}

\resumeSubHeadingListEnd

\end{document}